---
title: "CBM_defaults"
author: ""
date: "19 January 2018"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

# CBM_defaults

## Overview

The primary role of the CBM_defaults module is to read in various tables from the SQLite database file. This includes default disturbance data such as different disturbance types and their IDs, spinup parameters, pool names, and more. The outputs of this module are primarily used in CBM_dataPrep_x and CBM_core.

## List of input objects

| Name          | Class        | Description                       | Source     |
|----------------|----------------|-------------------------|----------------|
| Archive Index | SQL Database | SQLite database file for CFS_CBM3 | insert url |

## List of output objects

| Name              | Class      | Description                                   |
|------------------|------------------|------------------------------------|
| disturbanceMatrix | Data table | Default disturbance data                      |
| spinupSQL         | Data table | Parameters for CBM_core spinup event          |
| pooldef           | Character  | Defines pool types                            |
| poolCount         | Numeric    | Number of pool types                          |
| forestTypeID      | Data table | Defines forest types and their respective IDs |

## OLD VERSION

## Overview

This module can run independently by running the global script below. Its main task is to read-in all the default values in SpaDES-CBM which is akin to the `ArchiveIndex` in CBM-CFS3 runs.

## Usage

```{r module_deafults_usage, eval=FALSE}
if (!require("remotes")) {
  install.packages("remotes")
}
remotes::install_github("PredictiveEcology/Require@development")
remotes::install_github("PredictiveEcology/CBMutils@development")
library(Require)
Require("PredictiveEcology/SpaDES.project@transition", require = FALSE)
Require(c("SpaDES.core (>=1.1.0)", "SpaDES.tools (>= 1.0.0)",
          "googledrive", 'RCurl', 'XML'),
          #unlist(unname(packagesNeededInModules))),
        require = "SpaDES.core", # call `require` only on this package (same as `library`)
        verbose = 1)

cacheDir <- reproducible::checkPath("cache", create = TRUE)
moduleDir <- "modules"
inputDir <- reproducible::checkPath("inputs", create = TRUE)
outputDir <- reproducible::checkPath("outputs", create = TRUE)
setPaths(inputPath = inputDir, 
         modulePath = moduleDir, 
         outputPath = outputDir, 
         cachePath = cacheDir)

times <- list(start = 0, end = 10)
parameters <- list(
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("CBM_defaults")
objects <- list()
paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir
)

myDefaults <- simInit(times = times, params = parameters, modules = modules,
                      objects = objects, paths = paths)

outDefaults <- spades(myDefaults)
```

```{r tests, eval=FALSE}
# The spades call should make a "dataset" class object
testthat::expect_true(is(outSim@.envir$cbmData, "dataset"))
```

## Events

Describe what happens for each event type.

### Plotting

Write what is plotted.

### Saving

Write what is saved.

## Data dependencies

### Input data

How to obtain input data, and a description of the data required by the module. If `sourceURL` is specified, `downloadData("CBM_defaults", "path/to/modules/dir")` may be sufficient.

### Output data

Description of the module outputs.

## Links to other modules

Describe any anticipated linkages to other modules.
